---
title: Scatter Plots
author: Rebecca Voulgarakis
date: '2017-10-29'
slug: scatter-plots
categories:
  - R
tags:
  - plot
  - R Markdown
---

Let's start our data visualization adventures with the scatter plot. Hypothetically speaking, if we wanted to look at home runs vs. strikeouts for some of baseball's biggest stars, we could look at those relationships with a scatter plot.

First, we'll need to load the necessary packages for this session:
```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Let's say we only want to see home runs and strikeouts for players who had more than 500 home runs in their careers.
```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>500"

result<-sqldf(query)
```

This gives us all the players we want and stores the info as "result," which will make the process of visualizing the data easier. Speaking of which, let's visualize our data like so:

```{r}
ggplot()+
  geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3,color="blue")+
  ggtitle("Career Strikeouts vs. Home Runs for the Greatest Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Home Runs")
```

